Examining the effect of a trend on R*

### 2020-10-22 src/s_bivariate_normal.Rmd
nearly through trends

# Calculate R* dist
r_star_vals <- r_star_dist(full_samples)

g <- 
  qplot(r_star_vals) +
  xlab(TeX("$R*$")) +
  xlim(0.9, NA) +
  geom_vline(xintercept = 1, linetype=2) +
  ylab("Count") +
  theme(text=element_text(size=14, colour="black"),
        axis.text = element_text(colour="black"))
ggsave("../output/bivariate.pdf", g, width = 8, height = 6)
```

>>>>

# Calculate R* dist
r_star_vals_gbm <- r_star(full_samples, uncertainty = T, method = "gbm")
r_star_vals_rf <- r_star(full_samples, uncertainty = T, method = "rf")
mean(r_star_vals_gbm>1)
mean(r_star_vals_gbm)
mean(r_star_vals_rf>1)
mean(r_star_vals_rf)

g <- 
  tibble(RF=r_star_vals_rf, GBM=r_star_vals_gbm, iter=seq_along(GBM)) %>%
  melt(id.vars="iter") %>% 
  ggplot(aes(x=value, fill=as.factor(variable))) +
  geom_histogram(position = "identity", alpha=0.8) +
  xlab(TeX("$R*$")) +
  xlim(0.9, NA) +
  geom_vline(xintercept = 1, linetype=2) +
  ylab("Count") +
  theme(text=element_text(size=20, colour="black"),
        axis.text = element_text(colour="black")) +
  scale_fill_grey("Classifier")
ggsave("../output/bivariate.pdf", g, width = 8, height = 6)
```

### 2020-10-22 src/s_hyperparameters.Rmd
nearly through trends

Normal
```{r}
g1c <- readRDS("../data/hypers_normal_250.rds")$r_star %>% 
  melt(id.vars=c("int.depth", "n.trees")) %>% 
  group_by(int.depth, n.trees) %>% 
  summarise(lower=quantile(value, 0.25),
            middle=quantile(value, 0.5),
            upper=quantile(value, 0.75)) %>% 
  mutate(default=if_else(int.depth==3&n.trees==50, 1, 0)) %>% 
  ggplot(aes(x=as.factor(n.trees), y=middle, colour=as.factor(int.depth), group=as.factor(int.depth))) +
  geom_pointrange(aes(ymin=lower, ymax=upper, shape=as.factor(default)),
                  position=position_dodge2(width=0.1)) +
  geom_line(position=position_dodge2(width=0.1)) +
  xlab("# trees") +
  ylab("R*") +
  theme(text = element_text(size=16, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = c(0.7, 0.25)) +
  scale_y_continuous(limits=c(0.95, 2.8)) +
  geom_hline(yintercept = 1, linetype=2) +
  scale_color_brewer("Int. depth", palette = "Dark2") +
  guides(colour = guide_legend(nrow = 2, byrow = T)) +
  scale_shape(guide="none") +
  ggtitle("A. GBM")
```

@@

Normal
```{r}
g2c <- readRDS("../data/hypers_rf_normal_250.rds")$r_star %>%
  melt(id.vars="mtry") %>%
  group_by(mtry) %>%
  summarise(lower=quantile(value, 0.25),
            middle=quantile(value, 0.5),
            upper=quantile(value, 0.75)) %>%
  ggplot(aes(x=as.factor(mtry), y=middle, group=1)) +
  geom_pointrange(aes(ymin=lower, ymax=upper), position=position_dodge2(width=0.1)) +
  geom_line(group=1, position=position_dodge2(width=0.1)) +
  xlab(TeX("$m_{try}$")) +
  ylab("R*") +
  theme(text = element_text(size=16, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = c(0.7, 0.25)) +
  scale_y_continuous(limits=c(0.95, NA)) +
  geom_hline(yintercept = 1, linetype=2) +
  scale_color_brewer("Int. depth", palette = "Dark2") +
  guides(colour = guide_legend(nrow = 2, byrow = T)) +
  ggtitle("B. RF")
pdf("../output/hypers_normal_250.pdf", width = 12, height = 6)
multiplot(g1c, g2c, cols=2)
dev.off()
```

>>>>

Normal
```{r}
g1c <- readRDS("../data/hypers_normal_250.rds")$r_star %>% 
  melt(id.vars=c("int.depth", "n.trees")) %>% 
  group_by(int.depth, n.trees) %>% 
  summarise(lower=quantile(value, 0.25),
            middle=quantile(value, 0.5),
            upper=quantile(value, 0.75)) %>% 
  mutate(default=if_else(int.depth==3&n.trees==50, 1, 0)) %>% 
  ggplot(aes(x=as.factor(n.trees), y=middle, colour=as.factor(int.depth), group=as.factor(int.depth))) +
  geom_pointrange(aes(ymin=lower, ymax=upper, shape=as.factor(default)),
                  position=position_dodge2(width=0.1)) +
  geom_line(position=position_dodge2(width=0.1)) +
  xlab("# trees") +
  ylab("R*") +
  theme(text = element_text(size=16, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = c(0.7, 0.25)) +
  scale_y_continuous(limits=c(0.95, 4.1)) +
  geom_hline(yintercept = 1, linetype=2) +
  scale_color_brewer("Int. depth", palette = "Dark2") +
  guides(colour = guide_legend(nrow = 2, byrow = T)) +
  scale_shape(guide="none") +
  ggtitle("A. GBM")
```

@@

Normal
```{r}
g2c <- readRDS("../data/hypers_rf_normal_250.rds")$r_star %>%
  melt(id.vars="mtry") %>%
  group_by(mtry) %>%
  summarise(lower=quantile(value, 0.25),
            middle=quantile(value, 0.5),
            upper=quantile(value, 0.75)) %>%
  mutate(default=if_else(mtry==22, 1, 0)) %>%
  ggplot(aes(x=as.factor(mtry), y=middle, group=1, shape=as.factor(default))) +
  geom_pointrange(aes(ymin=lower, ymax=upper), position=position_dodge2(width=0.1)) +
  geom_line(group=1, position=position_dodge2(width=0.1)) +
  xlab(TeX("$m_{try}$")) +
  ylab("R*") +
  theme(text = element_text(size=16, colour="black"),
        axis.text = element_text(colour="black"),
        legend.position = c(0.7, 0.25)) +
  scale_y_continuous(limits=c(0.95, 4.1)) +
  geom_hline(yintercept = 1, linetype=2) +
  scale_color_brewer("Int. depth", palette = "Dark2") +
  guides(colour = guide_legend(nrow = 2, byrow = T)) +
  scale_shape(guide="none") +
  ggtitle("B. RF")
pdf("../output/hypers_normal_250.pdf", width = 12, height = 6)
multiplot(g1c, g2c, cols=2)
dev.off()
```

### 2020-10-22 src/s_mvt_normal.Rmd
nearly through trends

# Get R* distribution
full_data <- rstan::extract(fit, permuted=F)
a_df <- tibble(samples_10000_cp=r_star_dist(full_data))

@@

full_data <- rstan::extract(fit, permuted=F)
r_star2 <- r_star_dist(full_data)

a_df <- a_df %>%
  mutate(samples_400=r_star2)

@@

r_star3 <- r_star_dist(full_data)

a_df <- a_df %>%
  mutate(samples_10000_ncp=r_star3)

saveRDS(a_df, "../output/mvt_fit_all_accuracy.rds")
a_df <- readRDS("../output/mvt_fit_all_accuracy.rds")

ga <- 
  a_df %>% 
  melt() %>% 
  ggplot(aes(x=value, fill=fct_relevel(as.factor(variable), "samples_400", "samples_10000_cp", "samples_10000_ncp"))) +
  geom_histogram(position="identity", alpha=0.8, bins=50) +
  scale_fill_grey("# draws", labels=c("400, cp", "10,000, cp", "10,000, ncp")) +
  xlab(TeX("$R*$")) +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  theme(text = element_text(size=18, colour="black"),
        legend.position = c(0.8, 0.75),
        axis.text = element_text(colour="black")) +
  ggtitle("A.")

@@

pdf("../output/mvt_three.pdf", width = 12, height = 8)
multiplot(ga, gb, ga2, gc, cols = 2)
dev.off()
```

>>>>

# Get R* distribution
full_data <- rstan::extract(fit, permuted=F)
a_df <- tibble(samples_10000_cp_gbm=r_star(full_data, uncertainty = T, method="gbm"),
               samples_10000_cp_rf=r_star(full_data, uncertainty = T, method="rf"))

@@

full_data <- rstan::extract(fit, permuted=F)
r_star2_gbm <- r_star(full_data, uncertainty = T, method="gbm")
r_star2_rf <- r_star(full_data, uncertainty = T, method="rf")

a_df <- a_df %>%
  mutate(samples_400_gbm=r_star2_gbm,
         samples_400_rf=r_star2_rf)

@@

r_star3_gbm <- r_star(full_data, uncertainty = T, method = "gbm")
r_star3_rf <- r_star(full_data, uncertainty = T, method = "rf")

a_df <- a_df %>%
  mutate(samples_10000_ncp_gbm=r_star3_gbm,
         samples_10000_ncp_rf=r_star3_rf)

saveRDS(a_df, "../output/mvt_fit_all_accuracy.rds")
a_df <- readRDS("../output/mvt_fit_all_accuracy.rds")
a_df_gbm <- a_df %>%
  select(contains("gbm")) %>% 
  rename(samples_10000_cp=samples_10000_cp_gbm,
         samples_400=samples_400_gbm,
         samples_10000_ncp=samples_10000_ncp_gbm) %>% 
  mutate(Classifier="A. GBM")
a_df_rf <- a_df %>%
  select(contains("rf")) %>% 
  rename(samples_10000_cp=samples_10000_cp_rf,
         samples_400=samples_400_rf,
         samples_10000_ncp=samples_10000_ncp_rf) %>% 
  mutate(Classifier="B. RF")

ga <- 
  a_df_gbm %>% 
  melt() %>% 
  ggplot(aes(x=value, fill=fct_relevel(as.factor(variable), "samples_400", "samples_10000_cp", "samples_10000_ncp"))) +
  geom_histogram(position="identity", alpha=0.8, bins=50) +
  scale_fill_grey("# draws", labels=c("400, cp", "10,000, cp", "10,000, ncp")) +
  xlab(TeX("$R*$")) +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  theme(text = element_text(size=18, colour="black"),
        legend.position = c(0.8, 0.75),
        axis.text = element_text(colour="black")) +
  ggtitle("A.")

@@

pdf("../output/mvt_three.pdf", width = 12, height = 8)
multiplot(ga, gb, ga2, gc, cols = 2)
dev.off()

# provide GBM vs RF results in supplementary
ga1 <- 
  a_df_gbm %>% 
  bind_rows(a_df_rf) %>% 
  melt() %>% 
  ggplot(aes(x=value, fill=fct_relevel(as.factor(variable), "samples_400", "samples_10000_cp", "samples_10000_ncp"))) +
  geom_histogram(position="identity", alpha=0.8, bins=50) +
  scale_fill_grey("# draws", labels=c("400, cp", "10,000, cp", "10,000, ncp")) +
  xlab(TeX("$R*$")) +
  ylab("Count") +
  geom_vline(xintercept = 1, linetype=2) +
  theme(text = element_text(size=18, colour="black"),
        legend.position = c(0.8, 0.75),
        axis.text = element_text(colour="black")) +
  facet_wrap(~Classifier)
ggsave("../output/mvt_gbm_vs_rf.pdf", ga1, width = 12, height = 8)

a_df_gbm %>% 
  bind_rows(a_df_rf) %>% 
  melt() %>% 
  group_by(Classifier, variable) %>% 
  summarise(value=mean(value)) %>% 
  pivot_wider(id_cols = "variable", names_from = "Classifier", values_from = "value")
```

### 2020-10-22 src/s_trends.Rmd
nearly through trends

```{r}
# g <- readRDS("../output/experiment_trends_one_dim.rds") %>% 
#   select(trend, iters, rep, dimension, Rstar_split, method) %>% 
#   unique() %>%
#   select(-rep) %>% 
#   melt(c("trend", "iters", "dimension", "method")) %>% 
#   filter(variable=="Rstar_split") %>% 
#   ggplot(aes(y = value, x = trend)) + 
#   geom_jitter(aes(colour=as.factor(method))) + 
#   facet_grid(vars(iters), vars(dimension)) + 
#   geom_hline(yintercept = 1) +
#   theme(strip.text.x = element_text(size=16, colour="black"),
#         strip.text.y = element_text(size=16, colour="black"),
#         axis.text.x = element_text(size=16, colour="black"),
#         axis.text.y = element_text(size=16, colour="black"),
#         axis.title = element_text(size=16, colour="black")) +
#   xlab("Trend") +
#   ylab("Value")
# g
# 
# ggsave("../output/trends_one_dim.pdf", g, width = 8, height = 6)
```

@@

```{r}
g <- readRDS("../output/experiment_trends_joint_distribution.rds") %>%
  as.data.frame() %>%
  select(iters, rho, rep, zsRhat, Rstar_split, method) %>%
  unique() %>%
  select(-rep) %>%
  melt(c("rho", "iters", "method")) %>%
  mutate(value=as.numeric(as.character(value))) %>% 
  mutate(variable=case_when(variable=="zsRhat"~"A. Split-Rhat",
                            variable=="Rstar_split"~"B. Split-R*")) %>%
  ggplot(aes(y = value, x = rho)) +
  geom_jitter(aes(colour=as.factor(method))) +
  facet_grid(vars(iters), vars(variable)) +
  geom_hline(yintercept = 1) +
  theme(strip.text.x = element_text(size=16, colour="black"),
        strip.text.y = element_text(size=16, colour="black"),
        axis.text.x = element_text(size=16, colour="black"),
        axis.text.y = element_text(size=16, colour="black"),
        axis.title = element_text(size=16, colour="black")) +
  ylab("Value") +
  xlab(TeX("$\\rho$"))
g

>>>>

```{r}
g <- readRDS("../output/experiment_trends_one_dim.rds") %>%
  select(trend, iters, rep, dimension, Rstar_split, method) %>%
  unique() %>%
  select(-rep) %>%
  melt(c("trend", "iters", "dimension", "method")) %>%
  filter(variable=="Rstar_split") %>%
  ggplot(aes(y = value, x = trend)) +
  geom_jitter(aes(colour=as.factor(method))) +
  facet_grid(vars(iters), vars(dimension)) +
  geom_hline(yintercept = 1) +
  theme(strip.text.x = element_text(size=16, colour="black"),
        strip.text.y = element_text(size=16, colour="black"),
        axis.text.x = element_text(size=16, colour="black"),
        axis.text.y = element_text(size=16, colour="black"),
        axis.title = element_text(size=16, colour="black")) +
  xlab("Trend") +
  ylab("Value")
g

# ggsave("../output/trends_one_dim.pdf", g, width = 8, height = 6)
```

@@

```{r}
g <- readRDS("../output/experiment_trends_joint_distribution.rds") %>%
  as.data.frame() %>%
  select(iters, rho, rep, zsRhat, Rstar_split, method) %>%
  unique() %>%
  select(-rep) %>%
  melt(c("rho", "iters", "method")) %>%
  mutate(value=as.numeric(as.character(value))) %>% 
  mutate(variable=case_when(variable=="zsRhat"~"A. Split-Rhat",
                            variable=="Rstar_split"~"B. Split-R*")) %>% 
  mutate(iters=as.numeric(as.character(iters))) %>% 
  mutate(method=as.character(method)) %>% 
  mutate(method=if_else(method=="rf", "RF", "GBM")) %>% 
  ggplot(aes(y = value, x = rho)) +
  geom_jitter(aes(colour=as.factor(method))) +
  facet_grid(vars(iters), vars(variable)) +
  geom_hline(yintercept = 1) +
  theme(strip.text.x = element_text(size=16, colour="black"),
        strip.text.y = element_text(size=16, colour="black"),
        axis.text.x = element_text(size=16, colour="black"),
        axis.text.y = element_text(size=16, colour="black"),
        axis.title = element_text(size=16, colour="black")) +
  ylab("Value") +
  xlab(TeX("$\\rho$")) +
  scale_colour_grey("Classifier")
g
